Covariate analysis of MAYO reprocessed transcripts (with TMM normalisation and covariates adjusted)

### 2017-09-13 code/Rmd/MAYO_REPROCESSED_ISOFORM.Rmd
Added markdown to process MSSM isoforms

# Store logCPM
VOOM.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('Tx.ID') %>%
  write.table(file = 'MAYO_CBE_TCX_tpm.tsv', sep = '\t', row.names=F, quote=F)
LCOUNT_OBJ = File('MAYO_CBE_TCX_TPM.tsv', name = 'TPM (filtered)', parentId = CODE$properties$id)
annotations(LCOUNT_OBJ) = annotations(CODE)
annotations(LCOUNT_OBJ)$dataSubType = 'filteredLCPM'
LCOUNT_OBJ = synStore(LCOUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

>>>>

# Store logCPM
VOOM.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('Tx.ID') %>%
  write.table(file = 'MAYO_CBE_TCX_TPM.tsv', sep = '\t', row.names=F, quote=F)
LCOUNT_OBJ = File('MAYO_CBE_TCX_TPM.tsv', name = 'TPM (filtered)', parentId = CODE$properties$id)
annotations(LCOUNT_OBJ) = annotations(CODE)
annotations(LCOUNT_OBJ)$dataSubType = 'filteredLCPM'
LCOUNT_OBJ = synStore(LCOUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
